---
title: "Copying answers"
output: rmarkdown::html_vignette
description: >
  Learn how to copy answers between reviews and avoid redundant work.
vignette: >
  %\VignetteIndexEntry{Copying answers}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, setup, include=F}
library(assertthat)
library(glue)
library(rsr)
library(scales)
library(dplyr)
library(ggplot2)
library(knitr)

theme_538 = function(legend.pos="right"){
  theme(legend.title = element_blank(),
        legend.position = legend.pos,
        text = element_text(size=12)) 
}

knitr::opts_chunk$set(collapse = TRUE,comment = "#>",dev="svg",fig.ext = "svg")
```

Document reviews can eat a lot of time and often involve redundant work. Sysrev and rsr can help avoid duplicate work in document review.

This demo of reusability uses a sysrev of the parasitic disease [Echinococcosis](https://sysrev.com/p/111200) (ESR). ESR reviewed 31 articles and assigned values to 9 boolean labels. Sysrev provides a few methods for re-using article, labels and answers. Let's get started by pulling down the data from ESR and visualizing it:

```{r dev='svg'}
ESR.pid = 111200 # ESR id is 111200

# get 31 articles, 279 answers & 9 lbls
ESR.art = get_articles(ESR.pid) 
ESR.ans = get_answers(ESR.pid)  
ESR.lbl = get_labels(ESR.pid)   
```

```{r lbl-barplot,fig.width=8, fig.height=2, out.width="90%", out.height="300em",fig.align='center', echo=F, dpi=300}
tb = ESR.ans |> count(short_label,answer) |> inner_join(ESR.lbl,by="short_label")
ggplot(tb,aes(x=reorder(short_label,-project_ordering),y=n,fill=answer)) + 
  scale_fill_brewer("Cyl", palette = "Dark2") +
  coord_flip() + scale_y_continuous(expand=c(0,0)) +
  guides(fill=guide_legend(byrow = F)) +
  geom_col() +  xlab("") + ylab("") + 
  theme_538()
```

# Copying answers with code
**Some methods require sysrev technical support**

ESR articles and labels can be copied into a new project through cloning, and previous answers can be assigned through `rsr::review` or `rsr::copy_answers`. Below the ESR project is cloned into "Clone ESR" and some tests are run to confirm that the clone worked:

```{r clone-labels}
# clone ESR
CPY = clone_sysrev(ESR.pid,"Clone ESR")

# get cloned lbls & articles
CPY.lbl = get_labels(CPY$pid)   
CPY.art = get_articles(CPY$pid)
```

**`article_data_id`** is a shared article id. Since all articles are cloned from ESR, the article_data_id set in ESR should be the same as CPY:

```{r}
CPY.art$article_data_id |> 
  setequal(ESR.art$article_data_id)
```

**`global_label_id`** is a shared label id. Since all labels are cloned from ESR, the global_label_id set in ESR should be the same as CPY:

```{r}
ESR.lbl$global_label_id |> 
  setequal(CPY.lbl$global_label_id)
```

Projects sharing article_data_ids and global_label_ids can use `rsr::copy_answers` to copy answers from a source to a target. Running copy_answers can take a bit of time. 

```{r eval=F}
rsr::copy_answers(ESR.pid,CPY$pid)
```

Plotting results shows that `copy_answers` created a faithful duplication.

```{r compareplot, echo=F}
CPY.ans  = get_answers(CPY$pid)

tb  = ESR.ans |> count(short_label,answer) |> inner_join(ESR.lbl,by="short_label")
tb2 = CPY.ans |> count(short_label,answer) |> inner_join(CPY.lbl,by="short_label")
tb3 = rbind(tb |> mutate(sysrev="ESR"),tb2 |> mutate(sysrev="Clone ESR")) |> 
  select(sysrev,short_label,project_ordering,n,answer) |> 
  mutate(short_label = stringr::str_trunc(short_label,25,ellipsis = "…"))
```

```{r compare, fig.width=8, fig.height=2, out.width="90%", out.height="300em",fig.align='center', echo=F}
ggplot(tb3,aes(x=reorder(short_label,-project_ordering),y=n,fill=answer)) +
  scale_fill_brewer("Cyl", palette = "Dark2") +
  coord_flip() + scale_y_continuous(expand=c(0,0)) +
  facet_grid(~sysrev) +
  guides(fill=guide_legend(byrow = F)) +
  geom_col() +  xlab("") + ylab("") +
  theme_538()
```

# Copying answers on sysrev.com

<div style="position:relative;padding-bottom:56.25%;">
<iframe style="width:100%;height:100%;position:absolute;left:0px;top:0px;" frameborder="0" width="100%" height="100%" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture" allowfullscreen src="https://www.youtube.com/embed/eUllo6xwXLA"></iframe>
</div>

Final code from the video is below:

```{r eval=FALSE}
ESR.pid = 111200
CLN.pid = 115689

rsr::get_answers(ESR.pid)
ESR.lbl = rsr::get_labels(ESR.pid) |> 
  arrange(project_ordering) |> 
  select(short_label,global_label_id)

CLN.lbl = rsr::get_labels(CLN.pid) |> 
  arrange(project_ordering) |> 
  select(short_label,global_label_id)

ESR.art = rsr::get_articles(ESR.pid) |> select(aid,article_data_id)
CLN.art = rsr::get_articles(CLN.pid) |> select(aid,article_data_id)
rsr::copy_answers(ESR.pid,CLN.pid)

IMP.pid = 115697
IMP.lbl = rsr::get_labels(IMP.pid) |> 
  arrange(project_ordering) |> 
  select(short_label,global_label_id)

rsr::copy_answers(source.pid = ESR.pid, target.pid = IMP.pid)
```







































