---
title: "Track organization progress"
output: rmarkdown::html_vignette
description: >
  Learn how to track sysrev activity in an organization.
vignette: >
  %\VignetteIndexEntry{Track organization progress}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, setup, include = FALSE}
library(lubridate)
library(ggplot2)
library(purrr)
library(rsr)
library(geomtextpath)
library(tibble)
library(ggthemes)
library(DT)
library(dplyr)
library(tidyr)
library(knitr)

local({
  hook_plot = knit_hooks$get('plot')
  knit_hooks$set(plot = function(x, options) {
    x = paste(x, collapse = '.')
    if (!grepl('\\.svg', x)) return(hook_plot(x, options))
    # read the content of the svg image and write it out without <?xml ... ?>
    paste(readLines(x)[-1], collapse = '\n')
  })
})

mytheme = function (base_size = 12, base_family = "sans") 
{
    colors <- deframe(ggthemes::ggthemes_data[["fivethirtyeight"]])
    (theme_foundation(base_size = base_size, base_family = base_family) + 
        theme(line = element_line(colour = "black"), rect = element_rect(fill = colors["white"], 
            linetype = 0, colour = NA), text = element_text(colour = colors["Dark Gray"]), 
            axis.title = element_blank(), axis.text = element_text(), 
            axis.ticks = element_blank(), axis.line = element_blank(), 
            legend.background = element_rect(), legend.position = "none", 
            legend.direction = "horizontal", legend.box = "vertical", 
            panel.grid = element_line(colour = NULL), panel.grid.major = element_line(colour = colors["Medium Gray"]), 
            panel.grid.minor = element_blank(), plot.title = element_text(hjust = 0, 
                size = rel(1.5), face = "bold"), plot.margin = unit(c(1, 
                1, 1, 1), "lines"), strip.background = element_rect()))
}

knitr::opts_chunk$set(collapse = TRUE,comment = "#>",dev = 'svg', fig.ext=".svg", warning = F, message = F) 
# knitr::opts_chunk$set(cache = T,cache.path = "./cache")
```

Organizations can accumulate many users, projects, labels and answers. Keeping track of organization activity can be a real challenge. Here is a simple approach to tracking organization activity.

## Get Sysrevs
`rsr::get_sysrevs` gets all of the sysrevs for a given organization.

```{r results=F}
sysrevs = rsr::get_sysrevs("Ontox")
```
```{r echo=F}
sysrevs |> 
  select(project_id,name,roles) |> 
  print(,n=2)
```

The first project above can be found at (sysrev.com/p/77703). The project names, creation dates, and roles are available. 

## Roles
Project administrators can be discovered by unnesting the roles column. 

```{r eval=F}
sysrevs |> unnest(roles) |> filter(role=="admin")
```

```{r echo=F}
sysrevs  |> 
  unnest(roles) |> filter(role=="admin") |> 
  select(project_id,name,username,role) |> 
  print(n=2)
```

## Labeling activity
How active are the different projects? `get_answers` gets a projects answers. Run it on every project to get all organization answers. The `p.answers` function below guarantees that this section will run, even if get_answers breaks for some specific project. 

```{r results=F}
p.answers  = possibly(rsr::get_answers,otherwise = tibble())
sr.answers = sysrevs |> 
  select(project_id,name) |> 
  mutate(answers = map(project_id,p.answers)) |> 
  unnest(answers)
```

```{r echo=F}
sr.answers |> print(n=2)
```

### Project activity
A simple ggplot can now track project activity over time:

```{r echo=F, results=F,out.width="95%", fig.width=8,fig.height=4,fig.align='center',cache=F}
daily.answers = sr.answers |> 
  mutate(day = date(confirm_time)) |> 
  group_by(name,day) |> summarize(ans = n()) |> ungroup()

cumulative.answers = daily.answers |> 
  group_by(name) |> 
  arrange(day) |> mutate(ans = cumsum(ans)) |>
  filter(max(ans)>200) |> 
  ungroup()

ggplot(cumulative.answers,aes(x=day,y=ans,col=name,label=name)) + 
  geom_textline(text_smoothing = 60, size = 3, vjust=-1, fontface="bold") +
  geom_point(size=1,col="black") + mytheme()
```

### Labels

A table collecting all the labels and their usage can be generated:

```{r results=F}
labels = map_dfr(sysrevs$project_id,rsr::get_labels)
```

```{r echo=F}
labels |> 
  filter(is.na(root_label_id_local)) |> # remove child labels
  count(short_label,question,name="projects") |> # count projects with label
  arrange(-projects) |> 
  datatable()
```

